Scalar Feedback based Joint Time-Frequency Precoder interpolation for MIMO-OFDM Systems

### 2020-01-04 paper/main.tex
Minor changes in result section

Fig.~\ref{fig:ber_ped} compares the BER obtained using the proposed
quantization method with that obtained using exact precoders for a
$4\times 2$ 1024 subcarrier system a slow fading
($f_dT_s = 3.41 \times 10^{-6}$). The time based predictive approaches
correspond to temporal prediction using the manifold as well as scalar
parameter based approaches without utilizing the joint time-frequency
correlations. We can observe that the performance of the proposed
method tracks the performance with exact precoders over a wide range
of SNRs. This can be attributed to the fact that even the 1-bit update
to the scalar parameters is able to approximate the precoder very
accurately. Since the channel variation across subcarriers is gradual,
owing to the limited delay spread of the channel profile, linear
interpolation and prediction yields good performance. Moreover, this
method outperforms the Stiefel manifold based approach due to the fact
that the adaptation is much more accurate for scalar parameters than
the tangent space based adaptation used over the Stiefel manifold. The
obtained performance is close to the optimal precoder when speeds reduce.

Fig.~\ref{fig:ber_veh} shows a similar comparison for a similar
situation with a higher speed. The faster variation of the channel
taps with time necessitates the use of a smaller number of subcarriers
(viz. 64 subcarriers). The smaller number of subcarriers implies that
the predictive quantization and interpolation needs to be performed
across a larger frequency range, thereby potentially reducing the
accuracy. Even in this case, we observe that the scalar
parameter-based approach outperforms manifold based quantization by
about 1 dB for higher SNRs. Naturally, the rate of channel variation
is quite fast, which limits the efficacy of the proposed method in
tracking the channel parameters. In both the situations, the temporal-only
based interpolation using manifold has the poorest performance since it does
not utilize the joint time and frequency correlations.
\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{images/64final_withtime}
\caption{BER vs. SNR for QPSK transmission over the $4\times 2$ 64
  subcarrier MIMO-OFDM system, with the ITU Cost207-RA channel profile
  for $f_dT_s = 1.56\times 10^{-5}$, corresponding to a velocity of 172.8 km/h.}
\label{fig:ber_veh}
\end{center}
\end{figure}

@@

% \section{Acknowledgment}

>>>>

Fig.~\ref{fig:ber_ped} compares the BER obtained using the proposed
quantization method with that obtained using exact precoders for a
$4\times 2$ 1024 subcarrier system a slow fading
($f_dT_s = 3.41 \times 10^{-6}$). The time based predictive approaches
correspond to temporal prediction using the manifold as well as scalar
parameter based approaches without utilizing the joint time-frequency
correlations. We can observe that the performance of the proposed
method tracks the performance with exact precoders over a wide range
of SNRs. This can be attributed to the fact that even the 1-bit update
to the scalar parameters is able to approximate the precoder very
accurately. Since the channel variation across subcarriers is gradual,
owing to the limited delay spread of the channel profile, linear
interpolation and prediction yields good performance. Moreover, this
method outperforms the Stiefel manifold based approach due to the fact
that the adaptation is much more accurate for scalar parameters than
the tangent space based adaptation used over the Stiefel manifold. The
obtained performance is close to the optimal precoder when speeds reduce. 
Also, similar to results showed in \cite{Gupt1905:Predictive}, the joint time-frequency 
method outperforms the independent time-frequency method, illustrating the benefits of exploiting 
joint correlations versus just the independent correlations.

Fig.~\ref{fig:ber_veh} shows a similar comparison for a similar
situation with a higher speed. The faster variation of the channel
taps with time necessitates the use of a smaller number of subcarriers
(viz. 64 subcarriers). The smaller number of subcarriers implies that
the predictive quantization and interpolation needs to be performed
across a larger frequency range, thereby potentially reducing the
accuracy. Even in this case, we observe that the scalar
parameter-based approach outperforms manifold based quantization by
about 1 dB for higher SNRs. Naturally, the rate of channel variation
is quite fast, which limits the efficacy of the proposed method in
tracking the channel parameters.
\begin{figure}
\begin{center}
\includegraphics[width=0.35\textwidth]{images/64final_withtime}
\caption{BER vs. SNR for QPSK transmission over the $4\times 2$ 64
  subcarrier MIMO-OFDM system, with the ITU Cost207-RA channel profile
  for $f_dT_s = 1.56\times 10^{-5}$, corresponding to a velocity of 172.8 km/h.}
\label{fig:ber_veh}
\end{center}
\end{figure}

@@

\vspace{-10pt}
% \section{Acknowledgment}
